Resolvable Ambiguity

### 2019-07-11 paper/paper.tex
Improve formulation of theorem 6.1 and minor polish

For this section, we will use an alternative formulation of resolvable ambiguity for languages, stated in terms of interpretations instead of words:

\begin{theorem}
  A language given by $\parse : \T^{*} -> 2^T$ is resolvably ambiguous iff\\$\forall t \in T.\ \exists w \in \T^{*}.\ \parse(w) = \{t\}$.
\end{theorem}

@@

>>>>

For this section, we will use an alternative formulation of resolvable ambiguity for languages, stated in terms of parse trees instead of words:

\begin{theorem}
  Given an abstract parser $P = (\T, T, \parse)$, the language $L(P)$ is resolvably ambiguous iff $\quad\forall t \in T.\ \exists w \in \T^{*}.\ \parse(w) = \{t\}$.
\end{theorem}

@@

\subsubsection{Formalization}
